---
title: "Untitled"
output: html_document
date: "2023-11-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(readxl)

colors_mkt_cat<-c( "UNAPPROVED" = 'grey',
                   "UNAPPROVED HOMEOPATHIC" = '#a6cee3',
                   "UNAPPROVED DRUG OTHER" = '#1f78b4',
                   "BULK INGREDIENT - ANIMAL" = 'grey', #'#b2df8a',
                   "BULK INGREDIENT" = 'grey', #'#33a02c',
                   "LMUNADFMS"  = '#fb9a99',
                   "NADA" = 'grey30', #'#e31a1c',
                  
                   "Unapproved medical gas" = '#fdbf6f',
                   "unapproved other" = '#ff7f00',
                   "Conditional NADA" = "#009E73", #'#fb9a99',
                   "ANADA"= "#0072B2",
                   "drug for further processing" = 'grey', #'#b15928',
                   "export only" = 'grey' #'#ffff99'
                   )

colors_prod_type<-c( "OTC TYPE A MEDICATED ARTICLE ANIMAL DRUG" = 'grey80', #'#377eb8',
                    "VFD TYPE A MEDICATED ARTICLE ANIMAL DRUG"= 'grey30', #'#377eb8',
                   "BULK INGREDIENT - ANIMAL" = 'grey',
                   "BULK INGREDIENT - ANIMAL DRUG" = 'grey',
                   "BULK INGREDIENT" = 'grey',
                   "PRESCRIPTION ANIMAL DRUG" = 'grey30',#'#377eb8',
                   "OTC ANIMAL DRUG" = 'grey60', #'#377eb8',
                   "RECOMBINANT DEOXYRIBONUCLEIC ACID CONSTRUCT" = 'grey')



fxn_DT_base<-function(df){
   DT::datatable(
            df,
            
                            
                            extensions = 'Buttons',
                            class = 'cell-border hoover compact nowrap',
                            caption = '',
                            options = list(
                              fixedColumns = TRUE,
                              autoWidth = TRUE,
                              ordering = TRUE,
                              paging = TRUE, 
                              searching = TRUE,
                              dom = 'BSlfrtip', 
                              buttons = c('copy', 'csv', 'excel')
                              
                            ),
                            filter = list(
                              position = 'top', 
                              clear = FALSE
                            ),
                            rownames = FALSE
              )
}

```


#FDA facilities

<https://www.fda.gov/economics-staff/fda-glance>

```{r}
fda_facilities<-tibble(
  Year = c(2018, 2020, 2021, 2023, 2024),
  Domestic = c(1403, 1608, 1858, 980, 974), 
  Foreign = c( 385, 1156, 1103, 701, 753),
  Total = c(1788, 2764, 2961, 1681, 1727)
)%>%
  pivot_longer(cols = c(Domestic, Foreign), 
               names_to = 'Location', 
               values_to = 'Facility Count')%>%
  mutate(pct = `Facility Count`/Total)%>%
  mutate(Year = factor(Year))

ggplot(fda_facilities)+
    geom_bar(data = fda_facilities%>%
               select(Year, Total)%>%
               distinct(), 
             aes(x = Year, y =`Total`), stat = 'identity')+

  geom_bar(aes(x = Year, y =`Facility Count`, fill = Location), , 
           stat = 'identity', position = 'dodge', width = .6)+
  geom_text(data = fda_facilities%>%
               select(Year, Total)%>%
               distinct(), 
             aes(x = Year, y =`Total`, label = paste0(Total)), 
            color = 'white', vjust = 1)+
  geom_text(data = fda_facilities%>%
              filter(Location %in% 'Domestic'), 
             aes(x = Year, y =`Facility Count`, label = paste0(`Facility Count`)), 
            color = 'white', vjust = 1, postion = 'dodge', hjust = 1, size = rel(2))+
  geom_text(data = fda_facilities%>%
              filter(!(Location %in% 'Domestic')),
             aes(x = Year, y =`Facility Count`, label = paste0(`Facility Count`)), 
            color = 'white', vjust = 1, postion = 'dodge', hjust = 0, size = rel(2))+
  
  theme_bw()+
  theme(text = element_text(color = 'black'))+
  labs(title = 'FDA Facilities - Animal Drugs', 
       caption = 'Data from: https://www.fda.gov/economics-staff/fda-glance')+
  scale_fill_manual(values = c('#1b9e77','#d95f02', 'grey'))

ggsave('FiguresAABP/FDAFacilities.jpg', height = 3, width = 5)

#--------------------------------------------
ggplot(fda_facilities)+
  geom_bar(aes(x = Year, y =`Facility Count`, fill = Location), ,
           stat = 'identity', position = 'dodge', width = .6)+

    geom_bar(data = fda_facilities%>%
               select(Year, Total)%>%
               distinct(), 
             aes(x = Year, y =`Total`), stat = 'identity')+

   geom_text(data = fda_facilities%>%
               select(Year, Total)%>%
               distinct(), 
             aes(x = Year, y =`Total`, label = paste0(Total)), 
            color = 'white', vjust = 1)+
  theme_bw()+
  theme(text = element_text(color = 'black'))+
  labs(title = 'FDA Facilities - Animal Drugs', 
       caption = 'Data from: https://www.fda.gov/economics-staff/fda-glance')+
  scale_fill_manual(values = c('#1b9e77','#d95f02', 'grey'))

ggsave('FiguresAABP/FDAFacilities_no_text.jpg', height = 3, width = 5)

```

# plot percent by location

In 2020 there were mutual recognition agreements: European Union, Switzerland, United Kingdom

https://www.fda.gov/international-programs/international-arrangements/mutual-recognition-agreements-mra

```{r}
ggplot(fda_facilities)+
  geom_point(aes(x = Year, y = pct, color = Location, group = Location), shape = 16, size = 5)+
  geom_smooth(aes(x = Year, y = pct, color = Location, group = Location))+
  theme_bw()+
   scale_fill_manual(values = c('#1b9e77','#d95f02', 'grey'))+
   scale_color_manual(values = c('#1b9e77','#d95f02', 'grey'))+
  labs(title = 'Percent of FDA Aproved\nAnimal Drug Manufacturing Facilities by Location', 
       caption = 'In 2020 mutual recognition programs were established')+
  scale_y_continuous(labels = scales::percent)+
  ylim(c(0,1))

ggsave('FiguresAABP/FDAFacilities_pct.jpg', height = 3, width = 5)


```


```{r}

```



#green original
```{r}

date_updated <-'Feb 27, 2026'

green<-read_csv("FDAGreenBook.csv", #Dec 1 2025

#green<-read_csv("Electronic_Animal_Drug_Product_Listing_Directory.csv", #Mar 2 2024
# green<-read_csv("Electronic_Animal_Drug_Product_Listing_Directory.csv", #Nov 23 2023
                col_types = cols(.default = col_character()))

```

#green clean
```{r}
green_clean<-green%>%
  mutate(`Application Number or Monograph ID` = case_when(
    (is.na(`Application Number or Monograph ID`))~'No Application', 
    TRUE~`Application Number or Monograph ID`
  ))%>%
  mutate(`Marketing Category` = case_when(
    (`Marketing Category` %in% c("bulk ingredient",  
                                 "Bulk ingredient", 
                                 "BULK INGREDIENT"))~'BULK INGREDIENT', 
     (`Marketing Category` %in% c("drug for further processing"))~'BULK INGREDIENT', 
        (`Marketing Category` %in% c(
                                 "bulk ingredient for animal drug compounding", 
                                 "Bulk Ingredient For Animal Drug Compounding", 
                                 "BULK INGREDIENT FOR ANIMAL DRUG COMPOUNDING" ))~'BULK INGREDIENT', 
      (`Marketing Category` %in% c("Export only", 
                                 "export only"))~'Export Only', 
    (`Marketing Category` %in% c("conditional NADA", 
                                 "Conditional NADA", 
                                 "CONDITIONAL NADA" ))~'Conditional NADA', 
     (`Marketing Category` %in% c("legally marketed unapproved new animal drugs for minor species",
                                  "Legally Marketed Unapproved New Animal Drugs for Minor Species",
                                  "LEGALLY MARKETED UNAPPROVED NEW ANIMAL DRUGS FOR MINOR SPECIES" ))~'LMUNADFMS',
        (`Marketing Category` %in% c("unapproved drug other",
                                     "Unapproved drug other", 
                                     "Unapproved Drug Other", 
                                     "UNAPPROVED DRUG OTHER"  ))~'UNAPPROVED', #'UNAPPROVED DRUG OTHER', 
    (`Marketing Category` %in% c("unapproved homeopathic",
                                 "UNAPPROVED HOMEOPATHIC",
                                 "Unapproved homeopathic",
                                 "Unapproved medical gas",
                                 "unapproved other"))~'UNAPPROVED', #'UNAPPROVED HOMEOPATHIC', 
    TRUE~`Marketing Category`
  ))
  # mutate(`Product Type` = factor(`Product Type`,
  #                                      levels = c("OTC ANIMAL DRUG",
  #                                                 "PRESCRIPTION ANIMAL DRUG",
  #                                                 "BULK INGREDIENT",
  #                                                  "BULK INGREDIENT - ANIMAL DRUG",
  #                                                 "RECOMBINANT DEOXYRIBONUCLEIC ACID CONSTRUCT",
  #                                                 "VFD TYPE A MEDICATED ARTICLE ANIMAL DRUG",
  #                                                 "OTC TYPE A MEDICATED ARTICLE ANIMAL DRUG"
  #                                                 )))%>%
  
  #summary and filters -----------------------------------
  # filter(!(is.na(`Application Number or Monograph ID`)))%>%
  # filter(`Marketing Category` %in% c('NADA','ANADA', 'Conditional NADA' ))%>%

n_distinct(green$`Application Number or Monograph ID`, na.rm = T)

```
#marketing categories

```{r}
sort(unique(green_clean$`Marketing Category`))
```

#overview plot

```{r}

green_plot_overview<-green_clean%>%
  rowid_to_column()%>%
  group_by(`Marketing Category`)%>%
  summarize(ct_row = sum(n()), 
            distinct_rowid = n_distinct(rowid))%>%
  ungroup()

ggplot(green_plot_overview)+
  geom_bar(aes( x  = reorder(`Marketing Category`, ct_row), y = ct_row, fill = `Marketing Category`),
           stat = 'identity')+
  scale_fill_manual(values = colors_mkt_cat)+
  coord_flip()+
  theme_bw()+
  xlab('Marketing Category (simplified)')+
  ylab('Count Rows in Green Book')+
  labs(title = 'FDA Green Book',
       subtitle = paste0(date_updated),
       caption = 'LMUNADFMS = Legally Marketed Unapproved New Animal Drugs for Minor Species')

ggsave('Figures/green_summary.jpg')

```


#green2
```{r}
green2_pre<-green_clean%>%
  group_by(`Product Type`, 
           `Marketing Category`, 
           `Application Number or Monograph ID`,
           `Ingredient List`, 
           `Non Proprietary Name`,
           `Proprietary Name`, 
           `Labeler Name`
           #`Inactivation Date`, `Reactivation Date`
           )%>%
  summarize(NDC = paste0(sort(unique(NDC)), collapse = ','),
            Date_Inactive = paste0(sort(unique(`Inactivation Date`)), collapse = ','),
            Date_reactivated = paste0(sort(unique(`Reactivation Date`)), collapse = ','),
            #APP_number = paste0(sort(unique(`Application Number or Monograph ID`)), collapse = ','), 
            #`Proprietary Name` = paste0(sort(unique(`Proprietary Name`)), collapse = ','), 
             #`Labeler Name` = paste0(sort(unique(`Labeler Name`)), collapse = ','), 
            links = paste0(sort(unique(`Link`)), collapse = ','), 
            ct_applications = n_distinct(`Application Number or Monograph ID`), 
            #ct_Labelers = n_distinct(`Labeler Name`),
            ct_rows = sum(n())#,
            #ct_ProprieteryName = n_distinct(`Proprietary Name`)
            )%>%
  ungroup()%>%
  mutate(prod_type_short = case_when(
        (`Product Type` %in% "INTENTIONAL ANIMAL GENOMIC ALTERATION")~"Genomic Alteration",
   (`Product Type` %in% "ANIMAL CELLS, TISSUES, AND CELL AND TISSUE BASED PRODUCT")~"Cell or Tissue Product",
    (`Product Type` %in% "BULK INGREDIENT")~'Bulk Drug', 
    (`Product Type` %in% "BULK INGREDIENT - ANIMAL DRUG")~'Bulk Drug', 
    (`Product Type` %in% "OTC ANIMAL DRUG")~'OTC - Non Feed', 
    (`Product Type` %in% "OTC TYPE A MEDICATED ARTICLE ANIMAL DRUG")~'OTC - Feed', 
    (`Product Type` %in% "PRESCRIPTION ANIMAL DRUG" )~'Prescription',
    (`Product Type` %in% "RECOMBINANT DEOXYRIBONUCLEIC ACID CONSTRUCT" )~'RECOMBINANT Product',
    (`Product Type` %in% "VFD TYPE A MEDICATED ARTICLE ANIMAL DRUG" )~'VFD',
    TRUE~`Product Type`
  ))


#--------------------------------

write_rds(green2_pre, 'greenbookdetails/green2.rds')
write_rds(green2_pre, 'FDAGreenBook/green2_pre.rds')

#------------------------------

green2<-green2_pre%>%
    filter(`Marketing Category` %in% c('NADA', 'ANADA'))


sort(unique(green2_pre$`Marketing Category`))
```

#green by Application
```{r}

green_app<-green_clean%>%
  group_by(`Product Type`, 
           `Marketing Category`, 
           `Application Number or Monograph ID`,
           `Ingredient List`, 
           `Non Proprietary Name`,
           #`Proprietary Name`, 
           #`Labeler Name`
           #`Inactivation Date`, `Reactivation Date`
           )%>%
  summarize(NDC = paste0(sort(unique(NDC)), collapse = ','),
            Date_Inactive = paste0(sort(unique(`Inactivation Date`)), collapse = ','),
            Date_reactivated = paste0(sort(unique(`Reactivation Date`)), collapse = ','),
            #APP_number = paste0(sort(unique(`Application Number or Monograph ID`)), collapse = ','), 
            `Proprietary Name` = paste0(sort(unique(`Proprietary Name`)), collapse = ','), 
             `Labeler Name` = paste0(sort(unique(`Labeler Name`)), collapse = ','), 
            links = paste0(sort(unique(`Link`)), collapse = ','), 
            ct_applications = n_distinct(`Application Number or Monograph ID`), 
            ct_Labelers = n_distinct(`Labeler Name`),
            ct_rows = sum(n()),
            ct_ProprieteryName = n_distinct(`Proprietary Name`)
            )%>%
  ungroup()%>%
  mutate(prod_type_short = case_when(
    (`Product Type` %in% "INTENTIONAL ANIMAL GENOMIC ALTERATION")~"Genomic Alteration",
      (`Product Type` %in% "ANIMAL CELLS, TISSUES, AND CELL AND TISSUE BASED PRODUCT")~"Cell or Tissue Product",
    (`Product Type` %in% "BULK INGREDIENT")~'Bulk Drug', 
    (`Product Type` %in% "BULK INGREDIENT - ANIMAL DRUG")~'Bulk Drug', 
    (`Product Type` %in% "OTC ANIMAL DRUG")~'OTC - Non Feed', 
    (`Product Type` %in% "OTC TYPE A MEDICATED ARTICLE ANIMAL DRUG")~'OTC - Feed', 
    (`Product Type` %in% "PRESCRIPTION ANIMAL DRUG" )~'Prescription',
    (`Product Type` %in% "RECOMBINANT DEOXYRIBONUCLEIC ACID CONSTRUCT" )~'RECOMBINANT Product',
    (`Product Type` %in% "VFD TYPE A MEDICATED ARTICLE ANIMAL DRUG" )~'VFD',
    TRUE~`Product Type`
  ))


```
#green by application - Approved
```{r}
green_approved<-green_app%>%
  filter(`Marketing Category` %in% c('NADA', 'ANADA', 'Conditional NADA', "LMUNADFMS"))

```


#plot green app
```{r}
ggplot(green_app)+
   geom_bar(aes(x = `prod_type_short`, y = ct_applications, 
               fill = `Marketing Category`), stat = 'identity', alpha = 10)+
  theme_bw()+
  theme(legend.position = 'right')+
  scale_fill_manual(values = colors_mkt_cat)+
  ylab('Number of Applications')+
  xlab('')+
  coord_flip()+
  labs(title = 'Green Book Items', 
       caption = 'Count represents a count of distinct Application Numbers or Citations\nData is grouped by Product Type, Marketing Category,\nIngredient List, and Non Proprietary Name\nUnapproved products have an Application Number of "No Application"')

ggsave('GreenBookOutput/plot_green_app.jpg', height = 5, width = 7)

```
#marketing type
```{r}

mkt_type<-green_approved%>%
  group_by(`Product Type`, prod_type_short)%>%
  mutate(`Total Applications` = n_distinct(`Application Number or Monograph ID`),
         `Total Proprietary Names` = n_distinct(`Proprietary Name`))%>%
  ungroup()%>%
  group_by(prod_type_short, `Product Type`, `Marketing Category`, `Total Applications`, `Total Proprietary Names`)%>%
  summarize(ct_row = sum(n()), 
            ct_props = n_distinct(`Proprietary Name`),
            ct_apps = n_distinct(`Application Number or Monograph ID`))%>%
  ungroup()%>%
  mutate(pct_apps = paste0(round(100*(ct_apps/`Total Applications`), digits = 0), '%'), 
         pct_props = paste0(round(100*(ct_props/`Total Proprietary Names`), digits = 0), '%'))
  



```

#plot green approved
```{r}
ggplot(green_approved)+
   geom_bar(aes(x = `prod_type_short`, y = ct_applications, 
               fill = `Marketing Category`), stat = 'identity', alpha = 10)+
  geom_text(data= mkt_type%>%
              filter(prod_type_short %in% 'Prescription')%>%
              filter(`Marketing Category` %in% 'NADA'), 
            aes(x = prod_type_short, y = ct_apps/2, 
                label = paste0(ct_apps, ' (', pct_apps, ')')), color = 'white')+
   geom_text(data= mkt_type%>%
              filter(prod_type_short %in% 'Prescription')%>%
              filter(`Marketing Category` %in% 'ANADA'), 
            aes(x = prod_type_short, y = ct_apps+300, 
                label = paste0(ct_apps, ' (', pct_apps, ')')), color = 'white')+
  theme_bw()+
  theme(legend.position = 'right')+
  scale_fill_manual(values = colors_mkt_cat)+
  ylab('Number of Applications')+
  xlab('')+
  coord_flip()+
  labs(title = 'Green Book Items', 
       caption = 'Count represents a count of distinct Application Numbers or Citations\nData is grouped by Product Type, Marketing Category,\nIngredient List, and Non Proprietary Name')

ggsave('GreenBookOutput/plot_green_approved.jpg', height = 5, width = 7)

table(green_approved$`Marketing Category`)

```



# plot mkt cat - by number of prop names
```{r}
ggplot(mkt_type)+
  geom_bar(aes(x = reorder(`Product Type`, `Total Proprietary Names`), y = `Total Proprietary Names`#, 
               #fill = `Product Type`
               ), 
           stat = 'identity', fill = 'grey', position = 'dodge')+
    geom_bar(data = mkt_type,
           aes(x = `Product Type`, y = ct_props,  fill = `Marketing Category`), stat = 'identity')+
    geom_text(data = mkt_type%>%
              filter(`Product Type` %in% c('PRESCRIPTION ANIMAL DRUG'))%>%
              filter(`Marketing Category` %in% c('NADA')),
            aes(x = `Product Type`, y = ct_props/2, label = paste0(pct_props, '\nNADA')), fontface = 'bold', color = 'white')+
    geom_text(data = mkt_type%>%
              filter(`Product Type` %in% c('PRESCRIPTION ANIMAL DRUG'))%>%
              filter(`Marketing Category` %in% c('ANADA')),
            aes(x = `Product Type`, y = `Total Proprietary Names`-(ct_props/2), label = paste0(pct_props, '\nANADA')), fontface = 'bold', color = 'white')+
  scale_fill_manual(values = colors_mkt_cat)+

  ylab('Number of Proprietary Names')+
  xlab('')+
  theme_bw()+
  theme(legend.position = 'none')+
  coord_flip()+
  labs(title = "Green Book Product Types")
 ggsave('GreenBookOutput/Product_Types_ct_props.jpg')
 
```

#plot details

```{r}
get_big_generics_detail<-green_approved%>%
  group_by(`Ingredient List`, `Marketing Category`, `Product Type` )%>%
  summarize(ct_applications = sum(ct_applications), 
            list_prop_names = paste0(`Proprietary Name`, collapse = ','), 
            list_manufacturer = paste0(`Labeler Name`, collapse = ','))%>%
  ungroup()

get_big_generics<-green_approved%>%
  group_by(`Ingredient List` )%>%
  summarize(ct_applications = sum(ct_applications), 
            list_prop_names = paste0(`Proprietary Name`, collapse = ','), 
            list_labeler = paste0(`Labeler Name`, collapse = ','))%>%
  ungroup()%>%
  filter(ct_applications>5)

get_big_generics2<-green_approved%>%
  group_by(`Ingredient List` )%>%
  summarize(ct_applications = sum(ct_applications), 
            list_prop_names = paste0(`Proprietary Name`, collapse = ','), 
            list_labeler = paste0(`Labeler Name`, collapse = ','))%>%
  ungroup()%>%
  filter(ct_applications<=5)%>%
  filter(ct_applications>1)


ggplot(get_big_generics)+
  geom_bar(aes(x = reorder(`Ingredient List`, ct_applications), y = ct_applications), 
           stat = 'identity')+
  geom_bar(data = get_big_generics_detail%>%
             filter(`Ingredient List` %in% get_big_generics$`Ingredient List`), 
           aes(x = reorder(`Ingredient List`, ct_applications), y = ct_applications,
               fill = `Marketing Category`), stat = 'identity')+
  coord_flip()+
  theme_bw()+
  theme(legend.position = 'right')+
  scale_fill_manual(values = colors_mkt_cat)+
  ylab('Number of Applications')+
  xlab('')

ggsave('GreenBookOutput/ingredient_applications.jpg')

ggplot(get_big_generics2)+
  geom_bar(aes(x = reorder(`Ingredient List`, ct_applications), y = ct_applications), 
           stat = 'identity')+
  geom_bar(data = get_big_generics_detail%>%
             filter(`Ingredient List` %in% get_big_generics2$`Ingredient List`), 
           aes(x = reorder(`Ingredient List`, ct_applications), y = ct_applications,
               fill = `Marketing Category`), stat = 'identity')+
  coord_flip()+
  theme_bw()+
  theme(legend.position = 'none')+
  scale_fill_manual(values = colors_mkt_cat)+
  ylab('Number of Applications')+
  xlab('')

ggsave('GreenBookOutput/ingredient_applications2.jpg')
  

```



```{r}

generics<-green2%>%
  arrange(`Ingredient List`)%>%
  group_by(`Ingredient List`, `Product Type`, `Marketing Category`)%>%
  summarize( 
            #marketing_category = paste0(sort(unique(`Marketing Category`)), collapse = ','), 
            brand_name = paste0(sort(unique(`Proprietary Name`)), collapse = ','),
            count_products = n_distinct(`Proprietary Name`), 
            ct_applications = n_distinct(`Application Number or Monograph ID`))%>%
  ungroup()

write_csv(generics, 'GreenBookOutput/green_book_examples.csv')
#write_rds(generics, 'shinyGreenbookGenerics/green_book_examples.rds')


# generics2<-%>%
#   filter(`Marketing Category` %in% c("ANADA,NADA" ))
# 
# write_csv(generics2, 'GreenBookOutput/tbl_generics2.csv')

generics_details<-green2%>%
  filter(`Marketing Category` %in% c('ANADA', 'NADA' ))%>%
  filter(`Ingredient List` %in% c(
    'IVERMECTIN',
    'ENROFLOXACIN',
    'TULATHROMYCIN',
    'PHENYLBUTAZONE',
    'FLUNIXIN MEGLUMINE',
    'SULFADIMETHOXINE',
    'BUTORPHANOL TARTRATE',
    'CHLORTETRACYCLINE CALCIUM',
    'KETAMINE HYDROCHLORIDE',
    'LINCOMYCIN HYDROCHLORIDE',
    'OXYTETRACYCLINE',
    'DEXMEDETOMIDINE HYDROCHLORIDE',
    'OXYTETRACYCLINE HYDROCHLORIDE',
    'FLORFENICOL',
    'IVERMECTIN; CLORSULON', 
    'RACTOPAMINE HYDROCHLORIDE',
    'TYLOSIN TARTRATE', 
    'CEFTIOFUR HYDROCHLORIDE', 
    'DETOMIDINE HYDROCHLORIDE', 
    'DORAMECTIN', 
    'FUROSEMIDE', 
    'SULFAMETHAZINE', 
    'TYLOSIN PHOSPHATE', 
    'XYLAZINE HYDROCHLORIDE', 
    'CLOPROSTENOL SODIUM', 
    'DINOPROST TROMETHAMINE', 
    'EPRINOMECTIN', 
    'IVERMECTIN', 
    'MELENGESTROL ACETATE', 
    'MONENSIN', 
    'MOXIDECTIN', 
    'TILMICOSIN PHOSPHATE', 
    'TYLOSIN', 
    'AMPICILLIN TRIHYDRATE', 
    'CEFTIOFUR SODIUM', 
    'GONADORELIN DIACETATE TETRAHYDRATE', 
    'SPECTINOMYCIN', 
    'TILMICOSIN PHOSPHATE', 
    'XYLAZINE'
    ))
  write_csv(generics_details, 'GreenBookOutput/tbl_generics_details.csv')


```

# what generics exist as NADA/ANADA
```{r}

# df1<-generics2%>%filter(`Product Type` %in% c("OTC ANIMAL DRUG"))
# df2<-generics2%>%filter(`Product Type` %in% c("PRESCRIPTION ANIMAL DRUG"))
# df3<-generics2%>%filter(!(`Product Type` %in% c("PRESCRIPTION ANIMAL DRUG", "OTC ANIMAL DRUG")))
# 
# fxn_plot_prop_name_counts<-function(df){
# ggplot(df)+
#   geom_bar(aes(x = reorder(`Ingredient List`, ct_applications), 
#                y = ct_applications, fill = `Product Type`), stat = 'identity', fill = 'grey')+
#     geom_bar(data = df%>%
#                filter(`Ingredient List` %in% generics_details$`Ingredient List`),
#              aes(x = reorder(`Ingredient List`, ct_applications), 
#                  y = ct_applications, fill = marketing_category), 
#              stat = 'identity', #fill = 'grey20', #'#0072B2'
#              )+
#   facet_wrap(`Product Type`~., scales = 'free', ncol = 1)+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1), 
#         legend.position = 'top')+
#   xlab('')+
#     ylab('Count Applications')+
#    #scale_fill_manual(values = colors_mkt_cat)+
#   coord_flip()
#   #ggsave(file = paste0(plot_name))
# }
# 
# fxn_plot_prop_name_counts(df = df1)
# ggsave('GreenBookOutput/count_applications_OTC.jpg')
# 
# fxn_plot_prop_name_counts(df2%>%filter(ct_applications>5))
# ggsave('GreenBookOutput/count_applications_ScriptA.jpg')
# 
# fxn_plot_prop_name_counts(df2%>%filter(ct_applications<=5))
# ggsave('GreenBookOutput/count_applications_ScriptB.jpg')
# 
# fxn_plot_prop_name_counts(df3)
# ggsave('GreenBookOutput/count_applications_Feed.jpg')
# 
# 

```

# Enrofloxacin Generics
```{r}
# 
# flunixin<-green2%>%filter(str_detect(`Ingredient List`, 'FLUNIXIN|FLUNIXIN.|.FLUNIXIN|.FLUNIXIN.'))%>%
#   arrange(desc(`Marketing Category`))
# 
# write_csv(flunixin, 'GreenBookOutput/flunixin.csv')
# 
# enro<-green3%>%filter(str_detect(`Ingredient List`, 'ENROFLOXACIN|ENROFLOXACIN.|.ENROFLOXACIN|.ENROFLOXACIN.'))


```

# Parnell Drug Rep EDU

```{r}

active_ingredient_list <- c(
  "tulathromycin", "gamithromycin", "tildipironsin", "tilmicosin", "tylosin",
  "florfenicol", "oxytetracycline", "ceftiofur", "penicillin", 
  "ampicillin", "enrofloxacin", "danofloxacin", "pradofloxacin", 
  "sulfadiazine", "sulfadimethoxine", "sulfamethazine", "spectinomycin"
)

brd_ingredient_list <- c(
  "tulathromycin", "gamithromycin", "tildipironsin", 
  "florfenicol",  "enrofloxacin", "danofloxacin", "pradofloxacin"
)

# Collapse into one regex pattern
pattern <- str_c(active_ingredient_list, collapse = "|")
pattern_brd <- str_c(brd_ingredient_list, collapse = "|")

green_parnell <- green_clean %>%
  filter(!(`Marketing Category` %in% c("BULK INGREDIENT", "Export Only", "UNAPPROVED"))) %>%
  filter(str_detect(`Ingredient List`, regex(pattern, ignore_case = TRUE)))%>%
  select(-NDC, -contains('activation'), -`Marketing Category`, -`Non Proprietary Name`)%>%
  distinct()%>%
  filter(!(str_detect(`Proprietary Name`, regex("otic|flavored|22|27|veraflox|Osurnia|Component E|Component TE|Enroquin", ignore_case = TRUE))))%>%
  filter(!(str_detect(`Ingredient List`, 'FUROATE|BUTYL AL')))%>%
  filter(!(str_detect(`Product Type`, 'VFD')))%>%
  group_by(`Ingredient List`, `Product Type`, `Application Number or Monograph ID`, Link)%>%
  summarize(`Proprietary Name` = paste0(unique(`Proprietary Name`), collapse = ','), 
            `Labeler Name` = paste0(unique(`Labeler Name`), collapse = ',')
            )%>%
  ungroup()%>%
  mutate(`Antimicrobial Class` = 
           case_when(
            str_detect(`Ingredient List`, regex('tulathro|gamith|tildi|tilmicosin|tylosin', 
                                                ignore_case = TRUE))~'Macrolide', 
            str_detect(`Ingredient List`, regex('florfenicol', 
                                                ignore_case = TRUE))~'Amphenicol', 
            str_detect(`Ingredient List`, regex('enroflox|pradoflox|danoflox', 
                                                ignore_case = TRUE))~'Fluoroquinolone', 
             str_detect(`Ingredient List`, regex('ceftiofur|ampicillin|penicillin', 
                                                ignore_case = TRUE))~'BetaLactam/Cephalosporin', 
              str_detect(`Ingredient List`, regex('oxytetracycline', 
                                                ignore_case = TRUE))~'Tetracycline', 
             str_detect(`Ingredient List`, regex('spectinomycin', 
                                                ignore_case = TRUE))~'Aminocyclitol', 


             str_detect(`Ingredient List`, 'SULFA')~'Sulfonamide', 
            TRUE~'UnClassified'
             
           ))%>%
  mutate(BRD = case_when(
      str_detect(`Ingredient List`, regex(pattern_brd, ignore_case = TRUE))~'Main BRD Drug', 
      str_detect(`Proprietary Name`, 'Excede')~'Main BRD Drug',
      TRUE~'Other Drug')
      )

write_rds(green_parnell, 'data/green_parnell.rds')

green_parnell_simple<-green_parnell%>%
  mutate(`Proprietary Name` = str_replace(`Proprietary Name`, ' 25', ''))%>%
    mutate(`Proprietary Name` = str_replace(`Proprietary Name`, ' 100', ''))%>%

   group_by(`Antimicrobial Class`, `Ingredient List`, BRD)%>%
  summarize( count_PropName = n_distinct(`Proprietary Name`), 
            count_Labeler = n_distinct(`Labeler Name`),
            `Proprietary Name` = paste0(unique(`Proprietary Name`), collapse = ','), 
            `Labeler Name` = paste0(unique(`Labeler Name`), collapse = ',')
           
            )%>%
  ungroup()
write_rds(green_parnell_simple, 'data/green_parnell_simple.rds')

```

